**Results Template**

### 2021-09-27 1_descriptive.Rmd
lmer and descriptive (dt)

```{r}
ggplot(df, aes(yoni_total)) + geom_histogram()
ggplot(df, aes(BES_total)) + geom_histogram()
ggplot(df, aes(yoni_total, BES_total)) + geom_point()
ggplot(df, aes(HCT_accuracy)) + geom_histogram()
ggplot(df, aes(MAIA_total)) + geom_histogram()
ggplot(df, aes(HCT_accuracy, MAIA_total)) + geom_point()
```

>>>>

```{r independent var}
ggplot(df, aes(yoni_total)) + geom_histogram()
ggplot(df, aes(BES_total)) + geom_histogram()
ggplot(df, aes(yoni_total, BES_total)) + geom_point()
ggplot(df, aes(HCT_accuracy)) + geom_histogram()
ggplot(df, aes(MAIA_total)) + geom_histogram()
ggplot(df, aes(HCT_accuracy, MAIA_total)) + geom_point()
```

```{r dependent var}
ggplot(df, aes(instruction, DT_confidence)) + geom_boxplot()
ggplot(df, aes(instruction, DT_confidenceRT)) + geom_boxplot()
ggplot(df, aes(condition, DT_confidence)) + geom_boxplot()
ggplot(df, aes(condition, DT_confidenceRT)) + geom_boxplot()
```

```{r}
df.social <- df %>% filter(condition == 'Social')
ggplot(df.social, aes(yoni_total, DT_confidence_avg)) + geom_point()
ggplot(df.social, aes(BES_total, DT_confidence_avg)) + geom_point()

df.polyg <- df %>% filter(condition == 'Polygraph')
ggplot(df.polyg, aes(HCT_accuracy, DT_confidence_avg)) + geom_point()
ggplot(df.polyg, aes(MAIA_total, DT_confidence_avg)) + geom_point()
```

### 2021-09-27 index.Rmd
lmer and descriptive (dt)

```{r warning=FALSE, message=TRUE, results='asis'}
library(bayestestR)
library(parameters)
library(performance)
library(report)
library(see)
library(ggplot2)

>>>>

```{r warning=FALSE, message=TRUE, results='asis'}
library(bayestestR)
library(parameters)
library(performance)
library(report)
library(see)
library(ggplot2)
library(lme4)
library(modelbased)

### 2021-09-27 scripts/claudia/data processing.Rmd
lmer and descriptive (dt)

mydata <- data.frame()
for (participant in list.files("../../data/data_experimental")) {
  df_sub <- read.csv(paste0("../../data/data_experimental/", participant, "/deception/", participant, "_deceptiontask.csv"), header = FALSE)[-c(1:11), -c(5:34, 37:46, 48:54)] %>% 
    mutate(DT_trial = c(1:80)) %>% 
    mutate(DT_condition = c(rep("Social", 40), rep("Polygraph", 40)))
  mydata <- rbind(mydata, df_sub)
}

inclusion <- read.csv("../final_processing/Errors.csv") %>%
  rename(ID = ï..participant,
         DT_trial = Trial,
         inclusion = Inclusion,
         inclusion2 = Inclusion2)

data <- mydata %>% 
  rename(DT_item = V1,
       DT_style = V2,
       DT_instruction = V3,
       DT_question = V4,
       DT_confidence = V35,
       DT_confidenceRT = V36,
       ID = V47) %>%

  mutate(DT_confidence = as.numeric(DT_confidence)) %>% 
  mutate(DT_confidenceRT = as.numeric(DT_confidenceRT)) %>% 
  mutate(DT_instruction = as.factor(DT_instruction)) %>% 
  mutate(ID = as.numeric(ID)) %>% 
  left_join(inclusion) %>%

  select(ID, DT_trial, DT_condition, inclusion, inclusion2, everything()) #move columns to front

results <- data %>% 
  group_by(ID, DT_instruction, DT_style) %>% 
  summarise(DT_confidence_avg = mean(DT_confidence), DT_confidenceRT_avg = mean(DT_confidenceRT))

@@

```{r combine data}
data_combined <- read.csv("deceptiontask_extracted.csv") %>% 
  left_join(read.csv("yoni_processed.csv")) %>% 
  left_join(read.csv("BES_processed.csv")) %>% 
  select(-c(contains("Q"))) %>% 
  left_join(read.csv("HCT_processed.csv")) %>% 
  left_join(read.csv("MAIA2_processed.csv")) %>% 
  select(-c(contains("Q"))) %>% 
  left_join(read.csv("demo.csv")) %>% 
  select(-c(Name, Matric, HP, Email, Birthday, School, Course, LivedinSG))

>>>>

mydata <- data.frame()
for (participant in list.files("../../data/data_experimental")) {
  df_sub <- read.csv(paste0("../../data/data_experimental/", participant, "/deception/", participant, "_deceptiontask.csv"), header = FALSE)[-c(1:11), -c(5:34, 37:46, 48:54)] %>% 
    mutate(trial = c(1:80)) %>% 
    mutate(condition = c(rep("Social", 40), rep("Polygraph", 40)))
  mydata <- rbind(mydata, df_sub)
}

inclusion <- read.csv("../final_processing/Errors.csv") %>%
  rename(ID = ï..participant,
         trial = Trial,
         inclusion = Inclusion,
         inclusion2 = Inclusion2)

data <- mydata %>% 
  rename(item = V1,
       style = V2,
       instruction = V3,
       question = V4,
       DT_confidence = V35,
       DT_confidenceRT = V36,
       ID = V47) %>%

  mutate(DT_confidence = as.numeric(DT_confidence)) %>% 
  mutate(DT_confidenceRT = as.numeric(DT_confidenceRT)) %>% 
  mutate(instruction = as.factor(instruction)) %>% 
  mutate(ID = as.numeric(ID)) %>% 
  left_join(inclusion) %>%

  select(ID, trial, condition, inclusion, inclusion2, everything()) #move columns to front

results <- data %>% 
  group_by(ID, instruction, style) %>% 
  summarise(DT_confidence_avg = mean(DT_confidence), DT_confidenceRT_avg = mean(DT_confidenceRT))

@@

```{r combine data}
data_combined <- read.csv("deceptiontask_extracted.csv") %>% 
  left_join(read.csv("deceptiontask_processed.csv")) %>% 
  left_join(read.csv("yoni_processed.csv")) %>% 
  left_join(read.csv("BES_processed.csv")) %>% 
  select(-c(contains("Q"))) %>% 
  left_join(read.csv("HCT_processed.csv")) %>% 
  left_join(read.csv("MAIA2_processed.csv")) %>% 
  select(-c(contains("Q"))) %>% 
  left_join(read.csv("demo.csv")) %>% 
  select(-c(Name, Matric, HP, Email, Birthday, School, Course, LivedinSG))
